---
title: "Pins Demo"
author: "Jeremy Allen"
date: '2022-04-21'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pins

The pins package helps you publish data sets, models, and other R
objects, making it easy to share them across projects and with your
colleagues. The pin board can be on

-   local or temp folder
-   Shared folder (like Dropbox)
-   RStudio Connect
-   Amazon S3
-   Azure storage
-   Microsoft 365 (OneDrive and SharePoint) - Google Cloud

![flow diagram for using Pins with RStudio
Connect](example_pins_workflow.png)

```{r, eval=F, echo=T}

library(pins)
library(fs)

```

What version of pins are we using?

```{r, eval=F, echo=T}

packageVersion("pins")

```

## AWS S3 buckets

Note the use of environment variables for my key ID and key.

#### Create the board

```{r, eval=F, echo=T}

# Amazon AWS S3 board

bs3 <- board_s3(
  Sys.getenv("AWS_BUCKET"),
  prefix = "demo",
  versioned = TRUE,
  access_key = Sys.getenv("AWS_ACCESS_KEY_ID"),
  secret_access_key = Sys.getenv("AWS_SECRET_ACESS_KEY"),
  session_token = NULL,
  credential_expiration = NULL,
  profile = NULL,
  region = Sys.getenv("AWS_REGION"),
  endpoint = NULL,
  cache = NULL
)

```

#### What's already on the board in my S3 bucket

```{r, eval=F, echo=T}

# anything on there now?
bs3 %>% pin_list()

```

#### Write more to the board in my S3 bucket

```{r, eval=F, echo=T}

# write data frames to the board
bs3 %>% pin_write(islands)

```

pins wrote the data frame as an rds file

#### Interact with the pinned objects on the board

```{r, eval=F, echo=T}

bs3 %>% pin_list()

bs3 %>% pin_read("islands")

bs3 %>% pin_search(search = "CO2")

```

## RStudio Connect as a board

```{r eval=F, echo=T}

# RStudio Connect board

# make sure package rsconnect is already installed
brsc <- board_rsconnect(server = "colorado.rstudio.com")

# grab a coffee while this runs
brsc %>% pin_list()

brsc %>% pin_search(search = "codenames")

cn <- brsc %>% pin_read(name = "katie.masiello/codenames")

View(cn)

cache_info()

```

## Local board

```{r, eval=F, echo=T}

# Local board

blocal <- board_local() # share data across R sessions on the same computer

blocal %>% pin_write(mtcars)
blocal %>% pin_write(CO2)
blocal %>% pin_write(Orange)

blocal %>% pin_list()

# upload file instead of pinning R objects

pin_upload(
  board = blocal,
  paths = "msg.txt",
  name = "message_in_bottle",
  title = "Shared Bottle Message",
  description = NULL,
  metadata = NULL
)


blocal %>% pin_list()

# let's go to a new session and download that text file

```
